\documentclass[aspectratio=1610]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{MnSymbol}
\usepackage{stmaryrd}
\usepackage{colortbl}
\usepackage{caption}
\usepackage{comment}
\usepackage{pdfpages}
\usepackage{listings}
\usepackage{color}
\usepackage{booktabs}
\usepackage{soul}
\usepackage[normalem]{ulem}

\usepackage{tikz}
\usepackage{rotating}
\usepackage{amsmath}
\usetikzlibrary{arrows.meta} 

\usepackage{tcolorbox}
\usepackage{lipsum}
\usepackage{pgf}
\usepackage{etex}
\usepackage{tikz,pgfplots}
\usepackage{ragged2e}
\usepackage{subfig}
\usepackage{beamerthemesplit}
\usepackage{stmaryrd}
\usepackage{comment}
\usepackage{mathtools}
\usepackage[table]{xcolor}

\usetheme{metropolis}

\usepackage[style=authoryear,sorting=nyt]{biblatex}
\addbibresource{lit.bib}

\newenvironment{wideitemize}{\begin{itemize}\addtolength{\itemsep}{10pt}}{\end{itemize}}
\usepackage{appendixnumberbeamer} % For backup slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setbeamertemplate{footline}{
  \leavevmode%
  \hbox{%
    \begin{beamercolorbox}[wd=.4\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
      \usebeamerfont{author in head/foot}\insertshortauthor
    \end{beamercolorbox}%
    \begin{beamercolorbox}[wd=.6\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
      \usebeamerfont{title in head/foot}\insertshorttitle\hspace*{3em}
      \insertframenumber{} / \inserttotalframenumber\hspace*{1ex}
    \end{beamercolorbox}%
  }%
  \vskip0pt%
}
\setbeamertemplate{navigation symbols}{}

\definecolor{mybgcolor}{RGB}{255, 255, 255}
\setbeamercolor{background canvas}{bg=mybgcolor}

\lstset{frame=tb,
  language=Java,
  aboveskip=2mm,
  belowskip=2mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=2
}

\title{Work-From-Home and the Wage Premium}
\author{Anna Lukianova and Mitchell Vald\'es-Bobes}
\date{28 August 2024}

\begin{document}

% Title slide
{
  \setbeamertemplate{footline}{}
  \begin{frame}
    \titlepage
  \end{frame}
}
\addtocounter{framenumber}{-1}

% Slide 1: Research Question and Motivation
\section{Research Question and Motivation}
\begin{frame}{Research Question and Motivation}
  \begin{itemize}
    \item [\textbf{Placeholder:}] Introduce the central research question.
    \item [\textbf{Placeholder:}] Explain the motivation behind the study.
  \end{itemize}
\end{frame}

% Slide 2: Empirical Evidence
\section{Empirical Evidence}
\begin{frame}{Empirical Evidence}
  \begin{itemize}
    \item [\textbf{Placeholder:}] Present key empirical findings.
    \item [\textbf{Placeholder:}] Discuss data sources and methodology.
  \end{itemize}
\end{frame}

% Slide 3: Model
\section{Model}
\begin{frame}{Model}
  \begin{itemize}
    \item [\textbf{Placeholder:}] Outline the theoretical model.
    \item [\textbf{Placeholder:}] Describe the assumptions and framework.
  \end{itemize}
\end{frame}

% Slide 4: Calibration and Results
\section{Calibration and Results}
\begin{frame}{Calibration and Results}
  \begin{itemize}
    \item [\textbf{Placeholder:}] Summarize the calibration process.
    \item [\textbf{Placeholder:}] Highlight the main results.
  \end{itemize}
\end{frame}

% Slide 5: Conclusion and Future Work
\section{Conclusion and Future Work}
\begin{frame}{Conclusion and Future Work}
  \begin{itemize}
    \item [\textbf{Placeholder:}] Summarize the conclusions.
    \item [\textbf{Placeholder:}] Outline future research directions.
  \end{itemize}
\end{frame}

% Appendix for backup slides
\appendix

\begin{frame}[plain]
  \centering
  \Huge Backup Slides
\end{frame}

\begin{frame}{Additional Appendix Slide}
  \begin{itemize}
    \item [\textbf{Placeholder:}] Extra details, robustness checks, or supplementary materials.
  \end{itemize}
\end{frame}

\end{document}
